### 2023-01-10 README.Rmd
fixed Blues-color selection bug

```{r, eval=FALSE}
install.packages("remotes")
remotes::install_github("mtennekes/cols4all", dependencies = TRUE)
```

>>>>

```{r, eval=FALSE}
# colorspace 2.1 required:
install.packages(https://rdrr.io/r/utils/install.packages.html)("colorspace", repos = "https://R-Forge.R-project.org")

# development (github) version of cols4all
install.packages("remotes")
remotes::install_github("mtennekes/cols4all", dependencies = TRUE)
```
